\section{Introduction}\label{sec:intro}
The objective of this project is to design a high performance inspection system, implement it using the microcontroller AT90USB 1287 and demonstrate the functionality. The design objective of the inspection system is to sort items of varying materials and colors into an appropriate bin in shortest time and with the greatest possible accuracy. 

The design uses the 8 bit 1 MHz AVR family microcontroller AT90USB 1287 as the heart of the system. A DC motor is used to drive the conveyor belt which moves the items to be sorted. A bipolar stepper motor is used to rotate and position the appropriate bin to collect the items when they fall from the conveyor at the end of travel. Three sensor stations which consists of optical, ferromagnetic and reflective sensors, are used to identify the type and color of the items on the conveyor and also to determine whether the item has reached the end of the conveyor. 

The implementation of the design calls for advanced coding of microcontrollers that includes set up the  timers, implement dynamic linked list using pointers, use interface circuits to control stepper motor and DC motor, generate PWM signal to control DC motor,  use interrupts and implement Analogue to Digital Converters. 

The possible challenges in the project includes identifying the characteristics of items using various sensors without any errors, use various interrupts in their appropriate context and tune the stepper motor speed and acceleration for collecting the items in the shortest possible time with no errors. Considering the limited time available, combining all the concepts learned in the course to design and implement a complex embedded system is indeed a challenging task.
