\section{Acknowledgments}\label{sec:intro}

This highly challenging embedded system design project would not have been possible without the ample guidance of course instructor Mr. Yuanye Chen and lab instructor Mr. Patrick Chang. The concepts required to complete the project were effectively introduced in sequence in the class and the same was implemented during the weekly lab sessions. So by the end of lab 4, we could gain a lot of knowledge about the microcontrollers and their functionalities and we were in a position to start our design project with confidence.

We are highly grateful to Mr. Patrick Chang for patiently listening to all our queries and guiding us to find the right answers from the manual. He sacrificed his weekends and opened the lab on all the weekends which helped us to spend more time on our project and complete it in time.
We would like to thank the University of Victoria and the Department of Mechanical Engineering for offering such a valuable course, for providing us the technical manuals and access to the Mechatronics lab and for providing other infrastructures such as the library, which helped us to successfully complete this design project.
Also, we would like to extend our gratitude to all the Teaching Assistants for helping us to complete our lab works and for extending their support in evaluating assignments, supervising the exams and for evaluating the demonstration of the inspection system. Finally, we would like to thank our coursemates for being kind enough to share the limited available stations and other resources at the lab.
